Luminance constancy under fixed geometry

### 2018-02-07 Draft2/draft2.tex
more edits

\keywords{color constancy, accuracy maximization analysis, supervised learning,
luminance}

@@

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
and the position of the observer (Fig.~\ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

@@

In this work, we assume the noisy response model to be a multivariate gaussian. For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$. We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.

{\bf Estimating labels:} The image labels are estimated using the Bayesian decoder as described above. First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$. We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$. To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$. The estimates value is the one that optimizes the cost function.

{\bf Error estimation:}
The error of the luminance estimates are quantified in terms of the relative error ($E_{\rm rel}$), defined as follows:
\begin{align}
E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
\end{align}
where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance.

@@

Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
The AMA receptive fields do an excellent job of predicting the target object luminance. The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
The relative error of estimation is ~15\%, which low compared to that of the naive model (~42\%) or the linear model on center pixel (~21\%).

@@

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We generated a dataset of multispectral images labeled by the reflectance of a target object in each image. These images were generated by a software pipeline developed for this work, that we call Virtual world color constancy (VWCC). This software creates 3D scene descriptors based on programatic information provided by the user. Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc. We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances. Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image. Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.

>>>>

\keywords{color constancy, luminance constancy, supervised learning}

@@

\section{Introduction}
The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose and the position of the observer (Fig.~\ref{fig:introSchematic}).
Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
The ability of a visual system to extract such a stable representation is called color constancy. Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.

@@

In this work, we assume the noisy response model to be a multivariate gaussian. For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$. We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be contrast normalized, i.e., ${|s_{kl}|=1}$.

{\bf Estimating labels:} The image labels are estimated using the Bayesian decoder as described above. First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$. We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$. To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$. The estimated value is the one that optimizes the cost function.

\subsection{Error estimation}
If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.

@@

Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
The AMA receptive fields do an excellent job of predicting the target object luminance. The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
The relative error of estimation is $\sim15\%$, which low compared to that of the naive model ($\sim42\%$) or the linear model on center pixel ($\sim21\%$).

@@

\section{Discussion} \label{Discussion}
In this paper, we studied luminance constancy using naturalistic images. We generated a dataset of multispectral images labeled by the reflectance of a target object in each image. These images were generated by a software pipeline developed for this work that we call Virtual world color constancy (VWCC). This software creates 3D scene descriptors based on programatic information provided by the user. Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc. We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances. Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image. Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
